Field training 02 - Leaf traits measurements

### 2023-06-13 submission_2/submission_2.qmd
added text for comparison to task4

>>>>

## Comparison to LEDA Database

Another task was to compare our LMA values with those from the LEDA database. There, the values were only available as SLA. So we had to convert them into LMA first. The result can be seen in the plots in the appendix. If several values were available for one plant, we calculated the mean value. For two plants no values were available in the LEDA database. Overall, our values are slightly higher than those in the database, but are very similar overall.
